### 2022-01-27 documentos/generators.tex
Frase agregada al párrafo de relación alphas-PCEGs
Primera frase de párrafo relación alphas-PCEGs corregida de nuevo

PCE generators may be characterized by its local action on every qubit 
in the system, and thus each of them be denoted as $\mcG_{\vec\alpha}$, 
with $\vec\alpha$ each of the $4^{N}$ different vector indices.
% \cpnote{
The proof is simplified if one uses the Kraus representation developed in 
\sref{sec:kraus}, so we postpone the demonstration to appendix \ref{sec:2_qubits}.
For single qubits, the identity corresponds to $\mcG_0$, shown in 
\fref{fig:one:qubit:examples}(b), whereas $\mcG_3$ is shown in in 
\fref{fig:one:qubit:examples}(c).
% }
The 2-qubits PCE generator represented in subfigure (c)
of \Fref{fig:examplesPCE} acts on the first qubit (first column) as mapping its
Bloch sphere to de $x$-axis, and on the second qubit (first row) acts an identity,
hence it is labeled $\mcG_{(1,0)}$.
See \Fref{fig:appex:twoQ_PCEGs} for the notation of all 2-qubit PCE generators.

>>>>

PCE generators may be characterized by its local action on every qubit 
in the system. This action can be encoded in the same vector index $\vec\alpha$
introduced in \eqref{eq:pauli_strings}, hence each of the different $4^N$ 
vector indices may be related uniquely to each of the PCE generators
and thus denoted as $\mcG_{\vec\alpha}$.
% \cpnote{
The proof is simplified if one uses the Kraus representation developed in 
\sref{sec:kraus}, so we postpone the demonstration to appendix \ref{sec:2_qubits}.
For single qubits, the identity corresponds to $\mcG_0$, shown in 
\fref{fig:one:qubit:examples}(b), whereas $\mcG_3$ is shown in in 
\fref{fig:one:qubit:examples}(c).
% }
The 2-qubits PCE generator represented in subfigure (c)
of \Fref{fig:examplesPCE} acts on the first qubit (first column) as mapping its
Bloch sphere to de $x$-axis, and on the second qubit (first row) acts an identity,
hence it is labeled $\mcG_{(1,0)}$.
See \Fref{fig:appex:twoQ_PCEGs} for the notation of all 2-qubit PCE generators.
